*Prochlorococcus marinus* responses to light and oxygen

### 2024-03-06 Code/Manuscript_O2.Rmd
minor edits to readme and manuscript

@@

To Be Entered through PLoSONe system and deleted here
Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)

>>>>

XXX DOI pending from BOREALIS? or DRYAD? XXX

@@

To Be Entered through PLoSONe system and deleted here
Czech Academy of Science (OP) visiting fellowship supporting DAC work at AlgaTech
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship 2021 and 2022 (MS)
